---
title: "Hummingbird Resource Specialization"
author: "Ben Weinstein"
date: "Wednesday, November 26, 2014"
output:
  html_document:
    toc: true
    number_sections: true
---

#Aim

This is the master script that runs the data cleaning and baseline figures for the on going data collection at the Maquipucuna and Santa Lucia ecolodges.

#Version Control
This project can be cloned at github repo: 


```{r,echo=FALSE,warning=FALSE,message=FALSE}
library(knitr)
library(scales)
opts_chunk$set(fig.width=14,echo=FALSE,cache=TRUE,cache.path = 'Specialization_cache/', fig.path='figure/',warning=FALSE,message=FALSE, dpi=100)
```


```{r}
#setwd to dropbox
droppath<-"C:/Users/Ben/Dropbox/"
setwd(droppath)
#Set github path
gitpath<-"C:/Users/Ben/Documents/Maquipicuna/"
```

The first set of scripts are desciptive that clean, aggregate and quantify flowers, morphology, and hummingbird interactions.

#Data Cleaning

Each hummingbird and plant sighting comes with a GPS tag for spatial mapping. 

* These records need to be matched to the biodiversity data
* Remove duplicates
* Each data point should have a time stamp and elevation.

```{r,results='hide',fig.height=7}
source(paste(gitpath,"GPSMatching.R",sep=""))      
```

We measure corolla characteristics for each flower species along the elevation gradient. For this we need to:

* Clean taxonomy
* PCA of floral traits

```{r}
#source(paste(gitpath,"Nectar.R",sep=""))
#load("Thesis/Maquipucuna_SantaLucia/Results/Nectar.Rdata")
```

```{r phylogeny}
##Flower Phylogeny
#Using online tool Phylomatic (link), we can get the backbone of the phylogeny of the flowers
#source(paste(gitpath,"Phylogeny.R",sep=""))
#load("Thesis/Maquipucuna_SantaLucia/Results/Phylogeny/PhylogenyTropicos.Rdata")
```

#Flowers Transects

Twice a month we census the number of available hummingbird floral resources along the elevation gradient. 

* Taxonomic cleaning
* Mulitply number of stalks * inflorescences to estimate floral abundance
* Aggregate statistics on flowers/elevation over time

```{r,fig.height=10}
source(paste(gitpath,"FlowerTransects.R",sep=""))   
#Load from source:
#load("C:/Users/Ben/Dropbox/Thesis/Maquipucuna_SantaLucia/Results/FlowerTransect.Rdata")
```

##Plant Elevation ranges

* Match each observation with an observation
* plot elevation ranges

```{r elevation range plant,fig.height=12}
source(paste(gitpath,"GPSFlowerTransects.R",sep=""))   
```

#Hummingbird Transects
We conduct six elevation transects twice a month to estimate hummingbird diversity and distribution.

```{r Hummingbird transects,results='hide'}
source(paste(gitpath,"HummingbirdTransect.R",sep="")) 
#load("Thesis/Maquipucuna_SantaLucia/Results/HummingbirdTransect.Rdata")
```

#Hummingbird - Flower Interactions

Using both the hummingbird observation as well as time lapse cameras, we quantify the number of visits for each hummingbird to each flower species.

##Hummingbird Morphology

To measure the bill lengths of each hummingbird species, as well as other foot and wing traits to associate with flower visitation and behavior.

```{r}
#source(paste(gitpath,"Morphology.R",sep=""))
#load("Thesis/Maquipucuna_SantaLucia/Results/Morphology.Rdata")
```

##Hummingbird Elevation Range

Plot hummingbird and flower distribution over space and time
```{r time series,fig.height=8,fig.width=8}
source(paste(gitpath,"TimeSeries.R",sep="")) 
```
