Specialization and Plant - Hummingbird Interactions: Synopsis of Current Results
========================================================

Data Collection
-------
- Flower Transects (1300-2500m,  6 transects, 2x/Month) – Estimate the total available hummingbird resources

Q1: How do available resources change along the elevation gradient over time?
```{r, echo=FALSE,warning=FALSE,message=FALSE,fig.width=10,dpi=100,fig.height=8}
droppath<-"C:/Users/Jorge/Dropbox/"
setwd(droppath)
#Set github path
gitpath<-"C:/Users/Jorge/Documents/Maquipicuna/"
require(ggplot2)
load("Thesis/Maquipucuna_SantaLucia/Results/FlowerTransect.Rdata")

p<-ggplot(fl.totals,aes(x=Elev,TotalFlowers,col=Month.a)) + geom_point(size=3)  + stat_smooth(aes(group=Month.a),method="loess",se=FALSE) + facet_wrap(~Month.a,nrow=2) + theme_bw() + labs(col="Month")
p + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + ylab("# of Hummingbird Visited Flowers") + xlab("Elevation Range (m)")
```

Table of 10 most abundant hummingbird visited plants with total number of flowers records

```{r,message=FALSE,results='asis'}
require(xtable)

planttable<-aggregate(full.fl$Total_Flowers,by=list(toupper(full.fl$Family),full.fl$Iplant_Double),sum)

plantT<-na.omit(planttable[order(planttable$x),])
colnames(plantT)<-c("Family","Latin","Flowers")
print(xtable(plantT[1:10,]),type="html")
```

- Hummingbird Transects (1300-2500m,  6 transects, 2x/Month) – Collect geospatial data on hummingbird elevation ranges and interactions


- Hummingbird Flower Cameras (6am-6pm,2days,~30X/Month, placed at the most abundant flower resources)

- Flower Morphology (Corolla width, corolla length for majority of species, nectar concentration for a subset)

- Hummingbird Morphology (for all but 1 species, 17 morphological traits, from Gary Stiles)

- Flower Phylogeny (Genus Level phylogeny with branch lengths informed by the Angiosperm supertree)

-	Hummingbird Phylogeny (Both a molecular divergence and time tree are available for all species, from Jimmy McGuire)

-	Fine-scale temperature data (35 ibuttons were placed along the elevation transect to record temperature every hr for 1 year)

```{r}
summary(cars)
```

You can also embed plots, for example:

```{r fig.width=7, fig.height=6}
plot(cars)
```

