Using Taxize and Phylomatic
========================================================

For the script, i'm loading in an image, since the get_id call from topicos needs some user input, just to settle subspecies declarations in the database.
To avoid this in the markdown, just load an image that has previously performed this first block of code

```{r,results='asis'}
#Flower Phenology and Phylogenetics
#R script Ben Weinstein - Stony Brook University 7/7/2013
#Under Git repository - Maquipucuna

#Read in required libraries
require(taxize)
require(reshape2)
require(phytools)

#Set DropBox Working Directory
setwd("C:/Users/Ben/Dropbox/")

#gitpath<-"C:/Users/Ben/Documents/Maquipicuna/"

#need to run flowerTransects.R, get flower names from file
#fl.names<-read.csv("Thesis/Maquipucuna_SantaLucia/Results/FlowerTransects/Iplant_Names.txt",row.names=1)

#Grab those species that taxize recognizes

#Unfortunately, using the tropicos dp leads to lots of conflicts because of the number of subspecies, we just want rank = sp.
#Not a big deal, just can't show here.

#uids<-get_ids(gsub("_"," ",fl.names$x[-1]),db="tropicos",ask=TRUE)

#Save image, so we don't have to manually do that everytime.
#save.image("Thesis/Maquipucuna_SantaLucia/Results/Phylogeny/PhylogenyTropicos.Rdata")
```

Start code from here

```{r,message=FALSE}
setwd("C:/Users/Ben/Dropbox/")

#Optional start here on restart
load("Thesis/Maquipucuna_SantaLucia/Results/Phylogeny/PhylogenyTropicos.Rdata")

#Classify
class.taxize<-classification(uids$tropicos)

#Format into a dataframe
m.t<-melt(class.taxize,"ScientificName")

#Remove species with Na
m.t<-m.t[complete.cases(m.t),]

#Create list of plants to enter into Phylomatic
fl.leveln<-levels(factor(m.t$L1))

head(fl.leveln)

#Okay now we have the taxa list, let's first try the taxize:: function to access the phylomatic API
tree_smith <- phylomatic_tree(taxa=fl.leveln, storedtree='smith2011', get='POST')
tree_smith
plot(tree_smith)

tree_APG3 <- phylomatic_tree(taxa=fl.leveln, storedtree='R20120829"', get='POST')
tree_APG3
```

Okay, that didn't work, i'm not entirely sure if it was because the taxa don't match, there is an error in syntax, or that there isn't another resolution.

```{r}
#Just for fun, try genus only, in case its a species name problem?
# count number of words in a string
GenusOnly<-sapply(fl.leveln,function(x){
    split_x<-strsplit(as.character(x),split=" ")
    split_x[[1]][1]
  })

head(GenusOnly)

Gtree_smith <- phylomatic_tree(GenusOnly, storedtree='smith2011', get='POST')
Gtree_smith

tree_APG3 <- phylomatic_tree(taxa=GenusOnly, storedtree='R20120829"', get='POST')
tree_APG3
```

Not successful

**Try using the Phylomatic Website.**

I'm struggling a bit with the phylocom syntax since the sample is inconsistant, and it also disagrees with the documentation

Phylomatic sample input reads: malvaceae/durio/durio_zibethinus,
family/genus/genus_species
====================================================

Formatting for Phylomatic Online
---------------------------------

Go back to taxize classification, for each entry, format in Family/Genus/Genus_Species
```{r}
class.taxize[[5]]
names(class.taxize[5])
```

Loop through the classification, collecting the family genus and species (if there is a species name given)
===========

```{r,warning=FALSE,message=FALSE,syntaxloop}
phyloN<-vector()
for (i in 1:length(class.taxize)){
  y<-class.taxize[[i]]  
  
  #Skip if taxize didn't find a hit
  if(is.na(y)){next}
  
  GS<-gsub(" ","_",names(class.taxize[i]))
  
  #If there is not a species name
  if(length(y[y$Rank %in% "genus","ScientificName"])==0){
    phyloN[i]<-paste(y[y$Rank %in% "family","ScientificName"],GS,sep="/")}
  
  #If is genus, no species name
  if(!length(y[y$Rank %in% "genus","ScientificName"])==0){
    str1<-paste(y[y$Rank %in% "genus","ScientificName"],GS,sep="/")
    phyloN[i]<-paste(y[y$Rank %in% "family","ScientificName"],str1,sep="/")}
}

#remove Na's
phyloN<-phyloN[!is.na(phyloN)]

#View
head(phyloN)
```

Write to phylomatic output
```{r,PhyloWrite}
write.table(phyloN,paste(gitpath,"names.txt",sep=""),row.names=FALSE, col.names=FALSE,quote=FALSE)
```

#Read in phylomatic output 
---------------------------

```{r,PhyloMin}
#Try both the phytools and ape options, the phytools just hangs.
#tree<-read.newick(paste(gitpath,"PhyloM.txt",sep=""))
tree<-read.tree(paste(gitpath,"PhyloM.txt",sep=""))
```


Actual output file can be download and seen: 
------------------------------------
https://github.com/bw4sz/Maquipicuna/blob/master/phyloM.txt

```
